---
title: "week 9 tidyver/github lab"
author: "Chi Hang(Philip) Cheung"
date: "2024-11-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## R Markdown

Load data frame:
```{r cars}
url<- "https://raw.githubusercontent.com/stormwhale/data-mines/refs/heads/main/user_behavior_dataset.csv"
data<- read.csv(url)
```

String detect two key words: "pixel" and "galaxy".
data is piped into filter then combined with the function of str_detect to catch the desired character pattern.
```{r}
pi_gal<- data %>% 
  filter(str_detect(Device.Model,
                    regex("Pixel|Galaxy", ignore_case = TRUE)))
head(pi_gal)
```
To use str_extract to extract only numbers from a column mixed with characters:
"\\d+" is a regular expression for any digits
mutate is used to create a column to store the extracted numbers
```{r}
phone_gen<- data %>% 
  mutate(Phone_generation=str_extract(Device.Model, "\\d+")) %>% 
  select(c(Device.Model, Phone_generation))
head(phone_gen)
```
